Union and intersection contracts are hard, actually

### 2021-06-09 paper.tex
A modernised abstract

\begin{abstract}
This paper reports an attempt to incorporate union and intersection types in
Nickel, a configuration programming language with a gradual type system and
first-class contracts. While the end result looks appealing, it turns out the
concrete impact on both the design and the implementation of the language is
unexpectedly high. We review the issues raised in particular by the
implementation of contracts for unions and intersections, and why we think the
cost ends up too high for the benefit. We conclude by suggesting different leads
to represent and type unions.
\end{abstract}

>>>>

\begin{abstract}
Union and intersection types are a staple of gradually typed language such
as TypeScript. While it's long been recognized that union and
intersections types are difficult to verify statically, it may appear
at first that the dynamic part of gradual typing is actually pretty
simple.

It turns out however, that in presence of higher-order contracts union
and intersection is deceptively difficult. The literature on
higher-order contracts with union and intersection, while keenly aware
of the fact, doesn't really explain why. We point and illustrate the
problems and trade-offs inherent to union and intersection contracts,
via example and a survey of the literature.
\end{abstract}
